Realizing temporal graphs from fastest travel times

### 2023-09-22 STACS2023/STACS23-longversion.tex
STACS23 initial files

In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subset E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.

@@

\subsubsection{Preprocessing of the input}
From the underlying graph $G$ of $D$ we first create a graph $G'$ by
iteratively removing vertices of degree one from $G$,
and denote with 
\[
Z = V(G) \setminus V(G').
\]
Then we determine a minimum feedback edge set $F$ of $G'$.
%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
Note that $F$ is also a minimum feedback edge set of $G$.
Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
Let $V_1 \subset V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subset V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
and let $V_3 \subset V(G')$ be the set of vertices of degree at least $3$ in $T$. 
Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
and $|V_3| \leq |V_1|$ by the properties of trees.
We denote with 
\[U = V_1 \cup V_2 \cup V_3\]
the set of vertices of interest. It follows that $|U| \leq 4k$.
We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, since every neighbor of $u$ is the first vertex of a (unique) path to another vertex in $U$.
It follows that $|U^*| \in O(k^2)$.
From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
and call it a \emph{clip vertex of the tree $T_i$}.
It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
that are clipped at the same vertex $u_i \in V(G')$.
For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
and call it \emph{a representative vertex of the tree $T_{u_i}$}.
We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
\[
Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
\]
Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.

@@

        Note $R^{i-1} \subset R^x$.

>>>>

In a graph $G=(V,E)$, a \emph{feedback edge set} $F \subseteq E(G)$ is a subset of edges, such that each cycle in $G$ has at least one edge in $F$.
The minimum such set $F$ is called a  \emph{minimum feedback edge set} and its size, $k = |F|$, is called the \emph{feedback edge number} of graph $G$.
Note that one can find a minimum feedback edge set in linear time, by calculating a spanning tree (or forest) $T$ of the given graph $G$ and then removing all of the edges $T$ from $G$, \ie $F = E(G) \setminus E(T)$.

@@

\subsubsection{Preprocessing of the input}
From the underlying graph $G$ of $D$ we first create a graph $G'$ by
iteratively removing vertices of degree one from $G$,
and denote with 
\[
Z = V(G) \setminus V(G').
\]
Then we determine a minimum feedback edge set $F$ of $G'$.
%by finding a spanning tree $T$ of $G'$ and set $F = E(G) \setminus E(T)$. 
Note that $F$ is also a minimum feedback edge set of $G$.
Lastly, we determine sets $U$, of \emph{vertices of interest}, and $U^*$ of the neighbors of vertices of interest, in the following way.
Let $T$ be a spanning tree of $G'$, with $F$ being the corresponding feedback edge set of $G'$.
Let $V_1 \subseteq V(G')$ be the set of leaves in the spanning tree $T$, $V_2 \subseteq V(G')$ be the set of vertices of degree two in $T$, that are incident to at least one edge in $F$, 
and let $V_3 \subseteq V(G')$ be the set of vertices of degree at least $3$ in $T$. 
Then $|V_1| + |V_2| \leq 2k$, since every leaf in $T$ and every vertex in $V_2$ is incident to at least one edge in $F$,
and $|V_3| \leq |V_1|$ by the properties of trees.
We denote with 
\[U = V_1 \cup V_2 \cup V_3\]
the set of vertices of interest. It follows that $|U| \leq 4k$.
We set $U^*$ to be the set of vertices in $V(G') \setminus U$ that are neighbors of vertices in $U$, \ie 
\[U^* = \{v \in V(G') \setminus U  :  u \in U, v \in N(u)\}.\]
Again, using the tree structure, we get that for any $u \in U$ its neighborhood is of size $|N(u)| \in O(k)$, since every neighbor of $u$ is the first vertex of a (unique) path to another vertex in $U$.
It follows that $|U^*| \in O(k^2)$.
From the construction of $Z$ (by iteratively removing vertices of degree one from $G$)
it follows that $Z$ consists of disjoint trees $T_1, T_2, \dots$.
For a tree $T_i$ we denote with $u_i$ the vertex in $G'$ that is a neighbor of a vertex in $T_i$, 
and call it a \emph{clip vertex of the tree $T_i$}.
It follows that there can be many different trees $T_i$ that are incident to the same clip vertex $u_i \in V(G')$,
but each tree $T_i$ is incident to exactly one clip vertex $u_i \in V(G')$.
Since $u_i$ is the only vertex connecting all of the trees $T_i$ incident to it,
from now on we assume that a tree $T_{u_i}$ in $Z$ is a union of trees on vertices from $V(G) \setminus V(G')$,
that are clipped at the same vertex $u_i \in V(G')$.
For each of the trees $T_{u_i}$ in $Z$, we select one vertex $r_i$, that is a neighbor of the clip vertex $u_i$,
and call it \emph{a representative vertex of the tree $T_{u_i}$}.
We now define as $Z^*$ the set of representatives $r_i$ of trees $T_i \in Z$,
where the clip vertex $v_i$ of $T_i$ is a vertex of interest, \ie
\[
Z^* = \{ r_i  :  r_i \in T_i, \text{ where $T_i \in Z$, the clip vertex $u_i$ of $T_i$ is in $U$, and $r_i u_i \in E(G)$}\}.
\]
Since there are $O(k)$ vertices of interest, we get that $|Z^*| \in O(k)$.
Note that determining sets $U$, $U^*$, and $Z^*$ takes linear time.

@@

        Note $R^{i-1} \subseteq R^x$.
